### 2019-11-27 ic-journal/sos.tex
Synchronized all changes from .tex files

The CCS formalisation starts with type definitions for action,
relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
to $\mathscr{L}$ (the set of names for labels) used at the beginning
of Section~\ref{ss:ccs}. The
cardinality and the exact elements of this type depend on the type variable $\beta$
instantiated by the end user.
%  \hl{or further formalisations built upon the
% present one.} 
All \hl{labels} are divided into input and output ones.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
following syntax:
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting}
Intuitively, with reference to the CCS terminology reported in
Section~\ref{ss:ccs}, $\beta$ represents the set of \emph{names}, and
\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} turns names into
\emph{input
and output actions}. 
For instance, if the type $\beta$ is instantiated to \texttt{string}
(the type of all strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
action \hl{$\overline{b}$}, respectively.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of all visible actions, plus the invisible action $\tau$
(\texttt{tau}). For instace, the input action $a$ and output
action \hl{$\overline{b}$} of type \hl{\mbox{``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''}}
are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.

The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
expressions, has two type variables $\alpha$ and $\beta$
  corresponding
%
% \footnote{The order \hl{between} type variables $\alpha$ and $\beta$
%     \hl{can be} arbitrary. Our choice is aligned with the literature.
% For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
% and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
%  $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
% variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
% having the corresponding cardinalities $h$ and $k$.}
to  %$\mathscr{X}$ (
the set of agent variables %) 
and %$\mathscr{L}$ (
the
set of names % used for labels), 
respectively (indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
with respect to the choice of these two sets).
%
The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha},
  \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined
  inductively by the  HOL \texttt{Datatype} package}
(here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
  functions;   \hl{we have also formalised relabeling, though it is not
 discussed below}):
\begin{lstlisting}
Datatype: CCS = nil
              | var 'a
              | prefix ('b Action) CCS
              | sum CCS CCS
              | par CCS CCS
              | restr (('b Label) set) CCS
              | relab CCS ('b Relabeling)
              | rec 'a CCS
End
\end{lstlisting}
The above definitions allow us to use terms like \texttt{nil} and
\texttt{sum P Q} in HOL. Their correspondences with conventional CCS notations
in the literature are given in Table~\ref{tab:ccsoperator}, where
most CCS operators have also the more readable abbreviation forms,
either for end user or for \TeX{} outputs. (All
  formal theorems and definitions in this paper
  are generated from HOL4. Also, by default, all theorems are fully
  specialised, removing outermost universal quantifiers.)

@@

(\hl{see}~\citep[p.~219]{holdesc} for more details).

@@

The last SOS rule \texttt{REC} (Recursion)
 says that if we substitute all occurrences of the variable $A$ in $P$ to
$(\recu A P)$ and the resulting process has a transition to $P'$
with action $u$, then $(\recu A P)$ has the same
transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\;\;\HOLFreeVar{E}}'' is an abbreviation
for ``\HOLinline{\HOLConst{CCS_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
recursive function substituting all appearences of a free variable \hl{with} another CCS term.
For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
level without changing anything, e.g.
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
\end{alltt}
The only two insteresting cases are those for  agent variables and recursion:
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
\end{alltt}
The variable substitutions only affects free
variables: the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}'' is
bound and therefore the substitution ignores it.
% The actual substitution happens in case of
% ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being
% substituted (and if \HOLinline{\HOLConst{CCS_Subst}} can actually reach it).

A useful facility exploiting the interplay
between HOL4 and Standard ML (that follows an idea \hl{of} Nesi~\cite{Nesi:1992ve})
 is a \hl{recursive} ML function \hl{that takes} a CCS process and \hl{returns} a theorem indicating all
  direct transitions of the process \hl{(if the input process is
 infinitely branching, the function will not terminate).}
For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
possible \hl{(one-step)} transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
(\nil | \bar{a}.\nil)$, $(a.\nil | \bar{a}.\nil)
\overset{\bar{a}}{\longrightarrow} (a.\nil | \nil)$ and $(a.\nil | \bar{a}.\nil)
\overset{\tau}{\longrightarrow} (\nil | \nil)$.
To completely describe all possible transitions of \hl{the} process manually, the
following two facts should be proved: (1) there are indeed the three
  transitions mentioned above; (2) there \hl{is} no other
  \hl{transition}. For large CCS processes it is surprisingly tedious to manually derive
all the possible transitions and prove the non-existence of other transitions.
This shows the usefulness of appealing to an ML function
\texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
For instance, \hl{taking the input} $(a.\nil | \bar{a}.\nil)$ the function returns the
following theorem which describes all \hl{its one-step} transitions:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
   \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}
\end{alltt}

>>>>

The CCS formalisation starts with type definitions for action,
relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
to $\mathscr{L}$ (the set of names for labels) used at the beginning
of Section~\ref{ss:ccs}. The
cardinality and the exact elements of this type depend on the type variable $\beta$
instantiated by the end user.
All labels are divided into input and output ones.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
following syntax:
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting}
Intuitively, with reference to the CCS terminology reported in
Section~\ref{ss:ccs}, $\beta$ represents the set of \emph{names}, and
\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} turns names into
\emph{input and output actions}.
For instance, if the type $\beta$ is instantiated to \texttt{string}
(the type of all strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
action $\overline{b}$, respectively.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of all visible actions, plus the invisible action $\tau$
(\texttt{tau}). For instace, the input action $a$ and output
action $\overline{b}$ of type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.

The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
expressions, has two type variables $\alpha$ and $\beta$ corresponding%
% \footnote{The order between type variables $\alpha$ and $\beta$
%     can be arbitrary. Our choice is aligned with the literature.
% For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
% and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
%  $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
% variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
% having the corresponding cardinalities $h$ and $k$.}
to the set of agent variables
and the set of names
respectively (indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
with respect to the choice of these two sets).
%
The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is defined inductively by the HOL \texttt{Datatype} package
(here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
  functions; we have also formalised relabeling, though it is not
  discussed below):
\begin{lstlisting}
Datatype: CCS = nil
              | var 'a
              | prefix ('b Action) CCS
              | sum CCS CCS
              | par CCS CCS
              | restr (('b Label) set) CCS
              | relab CCS ('b Relabeling)
              | rec 'a CCS
End
\end{lstlisting}
The above definitions allow us to use terms like \texttt{nil} and
\texttt{sum P Q} in HOL. Their correspondences with conventional CCS notations
in the literature are given in Table~\ref{tab:ccsoperator}, where
most CCS operators have also the more readable abbreviation forms,
either for end user or for \TeX{} outputs. (All
  formal theorems and definitions in this paper
  are generated from HOL4. Also, by default, all theorems are fully
  specialised, removing outermost universal quantifiers.)

@@

(see~\citep[p.~219]{holdesc} for more details).

@@

The last SOS rule \texttt{REC} (Recursion)
 says that if we substitute all occurrences of the variable $A$ in $P$ to
$(\recu A P)$ and the resulting process has a transition to $P'$
with action $u$, then $(\recu A P)$ has the same
transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\;\;\HOLFreeVar{E}}'' is an abbreviation
for ``\HOLinline{\HOLConst{CCS_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
recursive function substituting all appearences of a free variable with another CCS term.
For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
level without changing anything, e.g.
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
\end{alltt}
The only two insteresting cases are those for  agent variables and recursion:
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
\end{alltt}
The variable substitutions only affects free
variables: the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}'' is
bound and therefore the substitution ignores it.
% The actual substitution happens in case of
% ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being
% substituted (and if \HOLinline{\HOLConst{CCS_Subst}} can actually reach it).

A useful facility exploiting the interplay
between HOL4 and Standard ML (that follows an idea of Nesi~\cite{Nesi:1992ve})
 is a recursive ML function that takes a CCS process and returns a theorem indicating all
  direct transitions of the process (if the input process is
 infinitely branching, the function will not terminate).
For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
possible (one-step) transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
(\nil | \bar{a}.\nil)$, $(a.\nil | \bar{a}.\nil)
\overset{\bar{a}}{\longrightarrow} (a.\nil | \nil)$ and $(a.\nil | \bar{a}.\nil)
\overset{\tau}{\longrightarrow} (\nil | \nil)$.
To completely describe all possible transitions of the process manually, the
following two facts should be proved: (1) there are indeed the three
  transitions mentioned above; (2) there is no other
  transition. For large CCS processes it is surprisingly tedious to manually derive
all the possible transitions and prove the non-existence of other transitions.
This shows the usefulness of appealing to an ML function
\texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
For instance, taking the input $(a.\nil | \bar{a}.\nil)$ the function returns the
following theorem which describes all its one-step transitions:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
   \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}
\end{alltt}
